Parsing Postfix log files

### 2007-12-17 doc/logparser.tex
Use .+ instead of .* in the generated regexes.

    \item [Classify words based on their frequency]  The frequency of each
        \textit{(word, word's position within the line)\/} tuple is
        checked: if its frequency is greater than the threshold supplied by
        the user (1\% of all lines is generally a good starting point) it
        is classified as a fixed word, otherwise it is classified as a
        variable term.  Variable terms are replaced by \texttt{.*}, which
        means to match zero or more of any character.

    \item [Build regexes]  The words are reassembled to produce a \regex{}
        matching the line, and a counter is maintained for each \regex{}.
        Contiguous sequences of \texttt{.*} in the newly reassembled
        \regexes{} are collapsed to a single \texttt{.*}; any resulting
        duplicate \regexes{} are combined, and their counters summed.  If
        the frequency of a \regex{} is lower than the threshold supplied by
        the user the \regex{} is discarded.\footnote{This is a second,
        independent threshold, but once again 1\% of input lines is a good
        starting point; obviously the threshold depends on the number and
        type of input lines.}  The new \regexes{} are printed for the user
        to add to the database, either as new rules or merged into the
        \regexes{} of existing rules; the counter for each \regex{} is also
        printed, giving the user an indication of how many of the input
        lines that \regex{} should match.  Discarding \regexes{} will
        result in some of the input lines not being matched; this utility
        should be run again once the unmatched lines have been isolated by
        running the parser, including the new \regexes{}, with the same
        input which produced the original set of unparsed lines.

>>>>

    \item [Classify words based on their frequency]  The frequency of each
        \textit{(word, word's position within the line)\/} tuple is
        checked: if its frequency is greater than the threshold supplied by
        the user (1\% of all lines is generally a good starting point) it
        is classified as a fixed word, otherwise it is classified as a
        variable term.  Variable terms are replaced by \texttt{.+}, which
        means to match zero or more of any character.

    \item [Build regexes]  The words are reassembled to produce a \regex{}
        matching the line, and a counter is maintained for each \regex{}.
        Contiguous sequences of \texttt{.+} in the newly reassembled
        \regexes{} are collapsed to a single \texttt{.+}; any resulting
        duplicate \regexes{} are combined, and their counters summed.  If
        the frequency of a \regex{} is lower than the threshold supplied by
        the user the \regex{} is discarded.\footnote{This is a second,
        independent threshold, but once again 1\% of input lines is a good
        starting point; obviously the threshold depends on the number and
        type of input lines.}  The new \regexes{} are printed for the user
        to add to the database, either as new rules or merged into the
        \regexes{} of existing rules; the counter for each \regex{} is also
        printed, giving the user an indication of how many of the input
        lines that \regex{} should match.  Discarding \regexes{} will
        result in some of the input lines not being matched; this utility
        should be run again once the unmatched lines have been isolated by
        running the parser, including the new \regexes{}, with the same
        input which produced the original set of unparsed lines.
